Generating the Blueprints of Java Ecosystem

### 2015-02-22 msr.tex

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)} \cite{CKJMDDS} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}. The version of the tool that we used for this experiment can be found in github~\cite{CKJM}.

>>>>

\begin{itemize}

  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of object-oriented metrics \cite{CHKE94}. The version of the tool that we used for this experiment can be found in github~\cite{CKJM}.
